### 2023-01-03 manuscript.rmd
Add Adrian's suggestions

authornote: |
  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.  The authors report there are no competing interests to declare.
  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/

@@

In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average [^pooling]. It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e. $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$. Instead of a single value, the regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group. It addresses the problem of clustering of articles by macro-level variables. This model is called the varying-intercept model and is used frequently in social science research. We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.

[^pooling]: One can also think about this in terms of pooling: how the data from different groups are combined. We can have complete pooling (the disaggregation approach, just one slope), no pooling (each group should be modelled individually and each group has a different slope), and partial pooling (each group does have a unique slope. But the distribution of all slopes follow a distribution).

The benefit of using multilevel modeling lies in its flexibility in handling multi-level data. Suppose we also want to consider the clustering of journalists around $o$ different media organizations in the above example and $j$-th media media organization of the $i$-th journalist, where $j = 1,\ldots, o$ and if such data were available. [^WJSOUTLET] The multilevel regression equations are rewritten as:

@@

Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field. Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@rinke:2018:PMA]. Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].

@@

What is the probability for this paper being accepted by *IJOC*? Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *IJOC*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate of a similar journal. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is mixed reviewed by three reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100%. If we (or other researchers) "repeat the experiment" and resubmit the same paper again to *IJOC*, the probability of the resubmitted paper for being accepted is 0%.

Without repeated experiment, these probabilities quantify our certainty on how likely the paper is being accepted, given the current available data . We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$). This can be summarized in the following equation [@gelman2020bayesian]:

@@

The $P(X| \theta)$ part is called likelihood function. In the *IJOC* example, the likelihood function is based on rough rules from our experience and thus is not systematic. In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC). Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), which require no elaboration, 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *IJOC* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. Finding previous studies for an informative prior is the logical first thing to do. @keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt. For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.

For the other six sevenths, one might not have any information to set an informative prior. One option is to consult experts or to make an educated guess. Expert elicitation is a way to probe how the experts in the field think about the hypotheses. A standardized protocol for expert elicitation is available [@hanea:2017:IDE] and there are many software tools available to facilitate the process [^experttools].

@@

But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors by experts’ judgment attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [e.g. @elff:2020:MAF].

@@

\begin{align}
  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} + \beta_{6} GDP_{k} + \epsilon_{i}
\end{align}

\begin{align}
  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} + \beta_{6} GDP_{k} \\ + \beta_{7} DEMO^2_{k} + \beta_{8} DEMO^3_{k} + \epsilon_{i}
\end{align}

@@

## Summary

@@

```{r fig3x, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
pp_check(import_brms, ndraws = 100)
```

## Summary

@@

First, the Bayesian interpretation of CIs is far more intuitive than the frequentist interpretation [@morey:2015]. Secondly, while all the models reported here can also be estimated within a frequentist framework, using a Bayesian framework and, more specifically, brms allows estimating them all with the same package. This also makes it easier to compare different competing models, as we have illustrated in our analysis. Third, comparing models and checking the predictive quality of the models is an essential part of a Bayesian framework. Of course, frequentist models can also be compared based on information criteria such as the BIC. However, PPCs that give by far the most detailed information about models and indicate in which area they potentially fail are only possible by using a Bayesian approach. Finally, while we discussed the question about priors as a potential challenge of Bayesian models, they are instead a strength of Bayesian models. Researchers must define priors to run a Bayesian regression analysis. As we could show, this limitation does not pose a controversial challenge as weakly informative priors can be chosen, and in most cases, enough data is available. Thus, the priors have almost no influence on the posterior distribution of the parameters. Moreover, if we have prior knowledge, it allows us to create even more useful models, as the first example has shown.

>>>>

authornote: |
  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (Hong Kong Baptist University) for sharing details about her study. The authors report there are no competing interests to declare.
  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/

@@

In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average. It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e. $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$. Instead of a single value, the regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group [^pooling]. It addresses the problem of clustering of articles by macro-level variables. This model is called the varying-intercept model and is used frequently in social science research. We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.

[^pooling]: One can also think about this in terms of pooling: how the data from different groups are pooled together. Complete pooling (the disaggregation approach, one slope for all groups), no pooling (each group is modelled individually and each group has a different slope), and partial pooling (each group has a unique slope. But the distribution of all slopes follows a distribution) are three scenarios. Multilevel modeling uses partial pooling.

The advantage of using multilevel modeling lies in its flexibility in handling multi-level data. Suppose we also want to consider the clustering of journalists around $o$ different media organizations in the above example and $j$-th media media organization of the $i$-th journalist, where $j = 1,\ldots, o$ and if such data were available. [^WJSOUTLET] The multilevel regression equations are rewritten as:

@@

Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field. Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@rinke:2018:PMA]. Unlike the frequentist confidence intervals, Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].

@@

What is the probability for this paper being accepted by *IJOC*? Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we could only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *IJOC*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate of a similar journal. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After months of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is mixed reviewed by three reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100%. If we (or other researchers) "repeat the experiment" and resubmit the same paper again to *IJOC*, the probability of the resubmitted paper for being accepted is 0%.

Without repeated experiment, these probabilities quantify our certainty on how plausible the paper is being accepted, given the current available data. We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$). This can be summarized in the following equation [@gelman2020bayesian]:

@@

The $P(X| \theta)$ part is called likelihood function. In the *IJOC* example, the likelihood function is based on rough rules from our experience and thus is not systematic. In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC) [^mcmcexplanation]. Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), which require no elaboration, 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.

[^mcmcexplanation]: How concretely MCMC can faciliate the estimation of likelihood function, given the data and prior, is too technical to be included in this paper. Readers can get an intuition of how it works in Chapter 8 of @mcelreath2020statistical. For how the method works in regression models, Chapters 9, 10, and 12 of @mcelreath2020statistical. For a comparative perspective between Bayesian and frequentist approaches, please refer to @samaniego2010comparison.

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *IJOC* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. Finding previous studies for an informative prior is the logical first thing to do. @keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt. For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially. For the other six sevenths, one might not have any information to set an informative prior. One option is to consult experts or to make an educated guess. Expert elicitation is a way to probe how the experts in the field think about the hypotheses. A standardized protocol for expert elicitation is available [@hanea:2017:IDE] and there are many software tools available to facilitate the process [^experttools]. But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors by experts’ judgment attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [e.g. @elff:2020:MAF].

@@

@@

\begin{align*}
  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i \\ + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} \\ + \beta_{6} GDP_{k} + \epsilon_{i} \\
  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i \\ + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} \\ + \beta_{6} GDP_{k} + \beta_{7} DEMO^2_{k} \\ + \beta_{8} DEMO^3_{k} + \epsilon_{i}\\
\end{align*}

@@

## Summary of Example 1

@@

```{r fig3x, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
pp_check(import_brms, ndraws = 100) + theme_minimal()
```

## Summary of Example 2

@@

First, the Bayesian interpretation of CIs is far more intuitive than the frequentist interpretation [@morey:2015]. Secondly, while all the models reported here can also be estimated within a frequentist framework, using a Bayesian framework and, more specifically, *brms* allows estimating them all with the same package. This also makes it easier to compare different competing models, as we have illustrated in our analysis. Third, comparing models and checking the data-generating quality of the models is an essential part of a Bayesian framework. Of course, frequentist models can also be compared based on information criteria such as the BIC. However, PPCs that give by far the most detailed information about models and indicate in which area they potentially fail are only possible by using a Bayesian approach. Finally, while we discussed the question about priors as a potential challenge of Bayesian models, they are instead a strength of Bayesian models. Researchers must define priors to run a Bayesian regression analysis. As we could show, this limitation does not pose a controversial challenge as weakly informative priors can be chosen, and in most cases, enough data is available. Thus, the priors have almost no influence on the posterior distribution of the parameters. Moreover, if we have prior knowledge, it allows us to create even more useful models, as the first example has shown.
